### 2009-03-31 docs/survival/survival.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@152 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@158 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

The density of a Weibull with range parameter $\gamma$ and shape parameter $\nu$ is 
\[
f(x;\gamma,\nu) =  \gamma \nu x^{\nu-1} \exp\left[-	\gamma x^\nu\right],
\]
and
\[
\int_0^x f(u;\gamma,\nu)du = 1-\exp(-\gamma y^\nu).
\]
If $\theta$ is the scale parameter in the parametrization of the Weibull in Wikipedia, then 
$\log(\gamma) = -\alpha\log(\theta)$

@@

Right censored observations:
\begin{align*}
pr(R_i, Z_i=0 | L_i) =& pr(T_i > R_i | T_i > L_i, Y_i =0) pr(Y_i =0)  + pr(Y_i =1)\\
=&pr(T_i > R_i) pr(Y_i = 0)/pr(T_i > L_i) + pr(Y_i =1)\\
=& \rho + (1-\rho) \left. \int_{R_i}^\infty f(x;\gamma_i, \nu) dx \right/\int_{L_i}^\infty f(x;\gamma_i, \nu) dx  \\
= &  \rho + (1-\rho) \left. \exp\left[-\gamma_i R_i^\nu\right] \right/\exp\left[-\gamma_i L_i^\nu\right]\\
= &  \rho + (1-\rho) \exp\left[-\gamma_i\left(L_i^\nu -R_i^\nu\right)\right] \\
\end{align*}

@@

\section{Other observations}
Untruncated right censored data or observed events can be seen as left truncated data with $L_i= 0$.  Left censored data can be regarded as interval censored data with $L_i = 0$.

Truncated and interval censored data are not exclusive.  An event can have three times, $M_i$ is the left truncation time, $L_i$ is the left censoring time, and $R_i$ is the right censoring time. Sometimes $M_i$ or $L_i$ or both are zero, or $R_i = \infty$.

Users could specify all 3 times, with $L_i =R_i$ for observed events.  R's Surv function specifies 2 times, and an option to indicate if it's interval censoring or  truncation.

>>>>

The density of a Weibull with range parameter $\gamma$ and shape parameter $\nu$ is 
\[
f(x;\gamma,\nu) =  \gamma \nu x^{\nu-1} \exp\left[-	\gamma x^\nu\right],
\]
and
\[
\int_x^\infty f(u;\gamma,\nu)du = \exp(-\gamma x^\nu).
\]
If $\theta$ is the scale parameter in the parametrization of the Weibull in Wikipedia, then 
$\log(\gamma) = -\alpha\log(\theta)$

@@

Right censored observations:
\begin{align*}
pr(R_i, Z_i=0 | L_i) =& pr(T_i > R_i | T_i > L_i, Y_i =0) pr(Y_i =0)  + pr(Y_i =1)\\
=&pr(T_i > R_i) pr(Y_i = 0)/pr(T_i > L_i) + pr(Y_i =1)\\
=& \rho + (1-\rho) \left. \int_{R_i}^\infty f(x;\gamma_i, \nu) dx \right/\int_{L_i}^\infty f(x;\gamma_i, \nu) dx  \\
= &  \rho + (1-\rho) \left. \exp\left[-\gamma_i R_i^\nu\right] \right/\exp\left[-\gamma_i L_i^\nu\right]\\
= &  \rho + (1-\rho) \exp\left[\gamma_i\left(L_i^\nu -R_i^\nu\right)\right] \\
\end{align*}

@@

\section{Other observations}

Right censored data, is right-censored left truncated with $L_i= 0$
\[
pr(T_i> R_i) = \rho + (1-\rho) \exp\left[\gamma_i\left( -R_i^\nu\right)\right]
\]

Left censored data is $pr(0<T_i < x)$ is interval censored data with $L_i=0$ and $R_i=x$.
